6.867 Problem Set 1

### 2015-12-10 Project/Latex/Paper.tex
[project] perplexity stuff.
[project] add graphs to latex
[project] remove equal sign.

 %% GRAPH AND TABLE HERE

@@

%

%% PUT PERPLEXITY DISTRIBUTIONS HERE

%

@@

Once we have constructed our full set of features, we aim to predict log(article pageviews), $\mathbf{y}$, using our full set of variables, which we include in our design matrix, $\mathbf{X}$. We estimate the feature weights using the closed form solution for both OLS and ridge regression:
\begin{equation}
\beta = (\mathbf{X}^T\mathbf{X} + \lambda \mathbf{I})^{-1}\mathbf{X}^T\mathbf{y}
\end{equation}
where $\mathbf{I}$ is the $k \times k$ identity matrix, and $\lambda$ is our regularization parameter. Setting $\lambda = 0$ corresponds to OLS, whereas non-zero values of $\lambda$ correspond to ridge regression. The motivation for performing ridge regression as opposed to OLS is to not overfit on our data.

@@

Since we also have Twitter data that tracks every tweet and retweet involving a NYT article, we would like to extend this project to also include our Twitter data. We can then explore many interesting potential cross effects, such as how does the article content predict the amount of Twitter sharing and alternately, how does content of a Tweet predict viewership.
=======
\section{Division of Labor}

>>>>

\begin{figure}[ht]
\includegraphics[width=\linewidth]{nall.png}
\caption{The negative average log-likelihood of the bigram and trigram models}
\label{fig:perp_hist}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=\linewidth]{perplexity.png}
\caption{The distribution of bigram and trigram perplexities}
\label{fig:perp_hist}
\end{figure}

@@

Once we have constructed our full set of features, we aim to predict log(article pageviews), $\mathbf{y}$, using our full set of variables, which we include in our design matrix, $\mathbf{X}$. We estimate the feature weights using the closed form solution for both OLS and ridge regression:
\begin{equation}
\beta = (\mathbf{X}^T\mathbf{X} + \lambda \mathbf{I})^{-1}\mathbf{X}^T\mathbf{y}
\end{equation}
where $\mathbf{I}$ is the $k \times k$ identity matrix, and $\lambda$ is our regularization parameter. Setting $\lambda = 0$ corresponds to OLS, whereas non-zero values of $\lambda$ correspond to ridge regression. The motivation for performing ridge regression as opposed to OLS is to not overfit on our data \cite{ridgeregressionNotes}.

@@

Since we also have Twitter data that tracks every tweet and retweet involving a NYT article, we would like to extend this project to also include our Twitter data. We can then explore many interesting potential cross effects, such as how does the article content predict the amount of Twitter sharing and alternately, how does content of a Tweet predict viewership.

\section{Division of Labor}
